% !TEX program = pdflatex
% Kush Dasadia — Resume
% Build:  pdflatex Kush_Dasadia_Resume.tex
%   or paste into Overleaf (zero install).

\documentclass[10pt,letterpaper]{extarticle}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=0.55in,bottom=0.55in,left=0.6in,right=0.6in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{tabularx}
\linespread{0.95}

% ---------- Colors ----------
\definecolor{ink}{HTML}{0A0A0A}
\definecolor{muted}{HTML}{5A5A5A}
\definecolor{faint}{HTML}{8A8A8A}
\definecolor{hairline}{HTML}{C9C9C9}
\definecolor{accent}{HTML}{B53826}

\color{ink}
\pagestyle{empty}
\setlength{\parindent}{0pt}

% ---------- Section heads ----------
\titleformat{\section}
  {\color{faint}\fontsize{9pt}{11pt}\selectfont\bfseries}
  {}{0pt}{}
  [\vspace{2pt}{\color{hairline}\hrule height 0.4pt}\vspace{2pt}]
\titlespacing*{\section}{0pt}{8pt}{3pt}

% ---------- Helpers ----------
% \role{Title}{Org}{Right text}
\newcommand{\role}[3]{%
  \vspace{2pt}%
  \noindent\begin{tabularx}{\linewidth}{@{}Xr@{}}%
    \textbf{#1} #2 & {\color{muted}\small #3} \\
  \end{tabularx}\par\vspace{0pt}%
}

% \project{Name}{Role/credit}{One-line description}
\newcommand{\project}[3]{%
  \vspace{3pt}%
  \noindent\textbf{#1}\;{\color{muted}\small\;\textperiodcentered\;#2}\\%
  {\color{muted}#3}\par\vspace{-3pt}%
}

\setlist[itemize]{leftmargin=14pt,topsep=1pt,itemsep=0pt,parsep=0pt}

% ---------- Document ----------
\begin{document}

% ----- Header -----
{\fontsize{22pt}{26pt}\selectfont\bfseries Kush Dasadia\par}
\vspace{1pt}
{\color{muted}\small
San Francisco \;\textperiodcentered\;
\href{mailto:kushdasadia@gmail.com}{kushdasadia@gmail.com} \;\textperiodcentered\;
\href{https://www.linkedin.com/in/kush-dasadia}{linkedin.com/in/kush-dasadia} \;\textperiodcentered\;
\href{https://x.com/Kush_Dasadia}{x.com/Kush\_Dasadia} \;\textperiodcentered\;
\href{https://fable.engineering}{fable.engineering}
}

\vspace{8pt}
{\fontsize{11pt}{15pt}\selectfont
Product builder at the intersection of AI and physical products.}

% ----- Education -----
\section{EDUCATION}

\role{University of California, Berkeley}{\;\textperiodcentered\; M.Eng, Mechanical Engineering}{Aug 2024 -- May 2025}
\vspace{-3pt}
{\color{muted}Concentration: Controls of Robotics \& Autonomous Systems.}

\role{Sardar Vallabhbhai National Institute of Technology (SVNIT), Surat}{\;\textperiodcentered\; B.Tech, Mechanical Engineering}{Jul 2019 -- Jun 2023}

% ----- Experience -----
\section{EXPERIENCE}

\role{Product Consultant}{\;\textperiodcentered\; Moxie Robots Inc.}{May 2026 -- present \;\textperiodcentered\; Palo Alto, CA}
\vspace{-3pt}
{\color{muted}Advising on the revival of Moxie, the Yves B\'{e}har / fuseproject-designed children's social robot. \textasciitilde10,000+ homes deployed; original company wound down late 2024.}
\begin{itemize}
  \item \textbf{Gen-2 product direction:} defining what the next product should be while preserving the personality, pace, and emotional intelligence of the original.
  \item \textbf{AI agent infrastructure:} long-horizon memory, multi-turn personality, mission and story framework, parental controls, on-device vs.\ cloud split, latency targets for face-to-face interaction.
  \item \textbf{Interaction experience:} pace, listening, expression, repair, age-appropriate scaffolding.
\end{itemize}

\role{Founder}{\;\textperiodcentered\; Fable Engineering}{Apr 2025 -- present \;\textperiodcentered\; San Francisco}
\vspace{-3pt}
{\color{muted}Operating company for hardware-first, AI-native product ventures. Pre-seed from The House Fund. Built and shipped five product lines across smart wearables, social robotics, kids' companions, and AI workflows (see Projects).}
\begin{itemize}
  \item \textbf{Hardware:} industrial design, 3D-printed prototype iteration loops, ODM sourcing at CES and in China, partnerships with European industrial design studios.
  \item \textbf{AI agent infrastructure:} voice + vision agent harnesses, planner / executor patterns, retrieval over personal context, structured eval harnesses, on-device vs.\ cloud split.
  \item \textbf{User research at scale:} 500+ interviews across creative professionals, students, robot-vacuum owners, and parents; synthesized findings into go / kill product decisions.
  \item \textbf{GTM:} LinkedIn beta launches, Reddit community building, 200+ outbound contacts, parallel customer discovery across multiple ICPs.
  \item \textbf{Fundraising:} closed Fable Engineering's pre-seed round (The House Fund); previously raised \$250K pre-seed for Companion Robots on the strength of a working droid prototype.
\end{itemize}

\role{Student Researcher}{\;\textperiodcentered\; MPC Lab, UC Berkeley (Prof. Francesco Borrelli)}{Aug 2024 -- May 2025 \;\textperiodcentered\; Berkeley, CA}
\vspace{-3pt}
\begin{itemize}
  \item Designed modular in-field morphing solutions for a 1/10-scale autonomous vehicle (US Navy capstone) using goosenecks to enhance performance in dynamic environments.
  \item Collaborated on control challenges and rapid design modifications across vehicle dynamics, materials engineering, 3D printing, and control theory.
\end{itemize}

\role{Sr. Drilling Officer (Company Man)}{\;\textperiodcentered\; Sun Petrochemicals, India}{Jul 2023 -- Jun 2024 \;\textperiodcentered\; India}
\vspace{-3pt}
\begin{itemize}
  \item Managed a 100+ engineer team across drilling, mud, cementing, and HSE functions on both onshore and offshore rigs (well depths 4,000--4,300 ft); owned end-to-end drilling projects from planning and equipment selection to fluid management, casing, and cementing operations.
  \item Coordinated rig contractors, mud engineers, cementing crews, vendors, and HSE leads; ran daily safety, performance, and cost reporting; held vendor selection, procurement, and budget accountability for active well programs.
\end{itemize}

\role{Virtual Research Intern}{\;\textperiodcentered\; Institute of Automotive Technology, TU Munich}{Feb 2022 -- Aug 2022 \;\textperiodcentered\; Remote / Munich}
\vspace{-3pt}
\begin{itemize}
  \item Conceptualized an automated charging system for battery-electric trucks; designed for compatibility, efficiency, and user-friendliness across multiple OEM platforms.
  \item Analyzed the heavy-duty EV charging landscape: emerging standards (CCS, MCS), depot vs en-route topologies, and integration trade-offs with grid and fleet operations.
\end{itemize}

% ----- Projects -----
\section{PROJECTS}
\vspace{2pt}
{\color{muted}\small Selected ventures built at Fable Engineering. Each is a distinct product line with its own thesis, prototype, and outcomes.}

\project{Super8}{Fable Engineering \;\textperiodcentered\; Product, Engineering, GTM \;\textperiodcentered\; \href{https://super8.so/landing}{super8.so}}{AI product visualization. Infinite-canvas, node-based agent that compiles natural-language intent into CAD / Blender / image-gen workflows.}
\begin{itemize}
  \item 250+ users, generating revenue.
  \item Designed the node-based canvas interface and the planner / executor agent; structured eval harness on fal.ai serverless infra (cold starts, shared pools, async submit-and-poll).
  \item Ran GTM across a LinkedIn beta launch, Reddit communities, and a 200-person outbound list; parallel customer discovery across growth marketers and industrial designers.
\end{itemize}

\project{Murmur}{Fable Engineering \;\textperiodcentered\; Full-stack hardware + software, User research}{Voice-enabled smart ring + AR-glasses bundle for ambient capture and contextual surfacing.}
\begin{itemize}
  \item \textbf{Traction:} 1,200+ waitlist; working prototype shipped to soft-launch users; AR-glasses + ring bundle live as Batch 01 reservations.
  \item \textbf{Hardware:} designed titanium enclosure and ran 3D-printed prototype iteration loop; sourced ODMs at CES and in China; partnered with a Belgian industrial design studio on the second-iteration enclosure.
  \item \textbf{Full stack:} ring firmware (BLE, audio, touch, power), backend (transcription, retrieval, async LLM), voice agent (planner / executor split), iOS companion app (capture, mind view, integrations: Notion / Calendar / Gmail / Slack / ChatGPT).
  \item \textbf{User research:} 500+ user interviews with creative professionals, students, and on-the-go workers.
\end{itemize}

\project{Zero}{Fable Engineering \;\textperiodcentered\; Hardware, Firmware, Industrial design}{Kid's desktop companion robot, built end-to-end in a 72-hour sprint.}
\begin{itemize}
  \item Hardware: Raspberry Pi 5 compute; 4.2" E-Ink face; dual speakers, camera, microphone, USB-C battery.
  \item Sprint methodology: Day 0 mood boards \textrightarrow{} Day 1 sketch \textrightarrow{} AI rendering \textrightarrow{} Fusion 360 CAD \textrightarrow{} overnight 3D print \textrightarrow{} Day 2 electronics + firmware bring-up \textrightarrow{} Day 3 vision + conversation integration.
  \item Event-driven Python service stack; lightweight on-device inference + remote LLM / VLM calls with guardrails.
\end{itemize}

\project{Sonic}{Fable Engineering \;\textperiodcentered\; Hardware, Mechanical design, Robot learning}{Low-cost semi-humanoid robotics platform built for AI / manipulation research and experimentation.}
\begin{itemize}
  \item Designed the torso frame and structural assemblies in CAD; 3D-printed parts for rapid iteration cycles.
  \item Selected off-the-shelf actuators across joints to keep BOM low while preserving DOF for manipulation experiments.
  \item Integrated and ran the $\pi_0$ vision-language-action foundation model (Physical Intelligence) on the platform; designed and conducted manipulation and behavior experiments.
\end{itemize}

\project{Formula Student (FSAE)}{SVNIT \;\textperiodcentered\; Powertrain Lead, Electric \& Combustion vehicles}{End-to-end powertrain design and integration for Formula SAE race cars across both EV and IC classes.}
\begin{itemize}
  \item \textbf{Combustion + Electric powertrain:} engine integration (intake / exhaust, fuel, cooling, ECU); motor + inverter selection; accumulator architecture (cells, series / parallel, BMS) and high-voltage safety per FSAE EV rules.
  \item \textbf{Drivetrain + simulation:} sized sprocket ratios, chain, and differential for 75 m accel / autocross / endurance trade-offs; MATLAB / Simulink acceleration model (motor torque, gearing, weight transfer, traction) validated sizing and streamlined dyno bench-testing.
  \item \textbf{Mechanical integration:} motor mounts, battery enclosure, cooling routing, drivetrain packaging within space-frame; calibration and on-track validation across the event profile.
\end{itemize}

% ----- Skills -----
\section{SKILLS}

\noindent\begin{tabularx}{\linewidth}{@{}p{1.35in}X@{}}
\textbf{AI \& agents}    & Voice + vision agent harnesses, planner / executor patterns, retrieval over personal context, structured eval, on-device vs.\ cloud split, fal.ai serverless. \\[2pt]
\textbf{Hardware}        & Industrial design, 3D printing, CAD (SolidWorks, Fusion 360, CATIA), Raspberry Pi, sensors, rapid prototype iteration loops. \\[2pt]
\textbf{Operations}      & ODM sourcing (CES, China), vendor \& partner management, user research at scale, GTM (LinkedIn, Reddit, outbound), cross-functional team leadership, end-to-end project execution, funding. \\[2pt]
\textbf{Programming}     & Python, MATLAB, Arduino, basic firmware bring-up. \\
\end{tabularx}

% ----- Publications & Patent -----
\enlargethispage{3\baselineskip}
\section{PUBLICATIONS \& PATENT}

\begin{itemize}
  \item Dasadia K., Gandhi M., Banerjee J. \emph{Numerical Validation of Power Take-off Damping in an OWC Chamber and Modifications for Increased Efficiency.} Springer Lecture Notes in Mechanical Engineering, 2022.
  \item Choukse P., Dasadia K., et al. \emph{Pipe Climbing Robot.} India Design Patent 337173001, 2021.
\end{itemize}

\end{document}
